Mode and tempo of promoter evolution as measured in the \textit{Paramecium aurelia} species complex

### 2019-03-08 manuscript.tex
Added italics to title.
New sentence to intro.

\title{Mode and tempo of promoter evolution as measured in the Paramecium aurelia species complex}

@@

\address{$^{1}$Biodesign Center for Mechanisms of Evolution\\
$^{2}$School of Life Sciences\\
Arizona State University, Office C445 797 E. Tyler Street, Tempe, AZ 85281}

@@

Genomic analysis across diverse eukaryotes has drawn attention to the important role of \textit{cis}-regulatory sequences in the evolution of gene expression \citep{Wittkopp:2008ki, Wittkopp:2011bc, Siepel:2014hd}. However, the \textit{cis}-regulatory sequence differences that accompany--or indeed underpin--species divergence remain largely unknown. A likely explanation for this is the difficulty in predicting \textit{cis}-regulatory regions from genomic sequence alone. Accurate estimation of promoter positions requires empirical, usually functional genomic evidence. At present, the best high-throughput approach to identify promoters at genome-scale is Transcription Start Site (TSS) profiling, which includes CAGE and RAMPAGE, among others. While TSS profiling methods differ methadologically, these methods capture the 5`-ends of capped mRNAs, sequence their corresponding cDNAs and align the reads to the genome to identify the TSSs present within a given transcriptome. Clustering of gene-adjacent TSSs defines a promoter, or transcription start region (TSR).

>>>>

\title{Mode and tempo of promoter evolution as measured in the \textit{Paramecium aurelia} species complex}

@@

\address{$^{1}$Biodesign Center for the Mechanisms of Evolution\\
$^{2}$School of Life Sciences\\
Arizona State University, 797 E. Tyler Street, Tempe, AZ 85281}

@@

Genomic analysis across diverse eukaryotes has drawn attention to the important role of \textit{cis}-regulatory sequences in the evolution of gene expression \citep{Wittkopp:2008ki, Wittkopp:2011bc, Siepel:2014hd}. However, the \textit{cis}-regulatory sequence differences that accompany--or indeed underpin--species divergence remain largely unknown. One plausible explanation for this is the difficulty in predicting \textit{cis}-regulatory regions from genomic sequence alone. Accurate estimation of promoter positions requires empirical, usually functional genomic evidence. At present, the best high-throughput approach to identify promoters at genome-scale is Transcription Start Site (TSS) profiling, which includes CAGE and RAMPAGE, among others. While TSS profiling methods differ among themselves methadologically, these methods capture the 5`-ends of capped mRNAs, sequence their corresponding cDNAs and align the reads to the genome to identify the TSSs present within a given transcriptome. Clustering of gene-adjacent TSSs defines a promoter, transcription start region (TSR), at single base-pair resolution, thereby providing genomic locations for \textit{cis}-regulatory regions within a species.\\
